The growth of children's semantic and phonological networks: insight from 10 languages

### 2019-02-06 journal/ms.Rmd
second version journal

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010]. Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow. Thus, cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014]. 
 <!--
\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
-->

@@

Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled. The plots show, overall, a negative correlation between the month of acquisition and the degree.  In production data, the average correlation across languages was `r ps_ave` ($SD=$`r ps_sd`) for the semantic networks and `r pp_ave` ($SD=$`r pp_sd`) for the phonological networks.  In comprehension data, the average correlation was `r cs_ave` ($SD=$`r cs_sd`) for the semantic networks and `r cp_ave` ($SD=$`r cp_sd`) for the phonological networks. These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English [@storkel2009; @hills2009] and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.

>>>>

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010;@lupyan2017]. Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow. Thus, cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014]. 
 <!--
\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
-->

@@

Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled. The plots show, overall, a negative correlation between the month of acquisition and the degree.  In production data, the average correlation across languages was `r ps_ave` ($SD=$ `r ps_sd`) for the semantic networks and `r pp_ave` ($SD=$ `r pp_sd`) for the phonological networks.  In comprehension data, the average correlation was `r cs_ave` ($SD=$ `r cs_sd`) for the semantic networks and `r cp_ave` ($SD=$ `r cp_sd`) for the phonological networks. These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English [@storkel2009; @hills2009] and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.

### 2019-02-06 journal/ms.tex
second version journal

Finally, we use developmental data in 10 languages. Lexical networks can
show more or less cross-linguistic variability along both the semantic
and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
et al., 2016). Besides, cultures might differ in the way caregivers talk
to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al.,
1997), and this difference in the input could influence the way in which
the children's networks grow. Thus, cross-linguistic comparison is
crucial to test what growth mechanism is cognitively universal and is
used by all children, and what mechanism is specific to some patterns of
learning that emerge due to the particulars of a given language or
culture (Bates \& MacWhinney, 1987; Slobin, 2014).

@@

Figures \ref{fig:corrProd} and \ref{fig:corrComp} show how the age of
production and comprehension, respectively, correlates with the degree
(or indegree for the semantic networks). For ease of visual comparison,
the predictor (i.e., the degree) was centered and scaled. The plots
show, overall, a negative correlation between the month of acquisition
and the degree. In production data, the average correlation across
languages was -0.24
(\$SD=\(0.10) for the semantic networks and -0.30 (\)SD=\(0.05) for the phonological networks. In comprehension data, the average correlation was -0.21 (\)SD=\(0.08) for the semantic networks and -0.21 (\)SD=\$0.07)
for the phonological networks. These results indicate that nouns with
higher degrees are generally learned earlier, thus replicating previous
findings in English (Hills et al., 2009; Storkel, 2009) and extending
these findings to 10 different languages, generally, in both production-
and comprehension-based vocabularies.

@@

\hypertarget{ref-macwhinney2014}{}
MacWhinney, B. (2014). \emph{The CHILDES project: Tools for analyzing
talk, volume ii}. Psychology Press.

>>>>

Finally, we use developmental data in 10 languages. Lexical networks can
show more or less cross-linguistic variability along both the semantic
and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Lupyan
\& Lewis, 2017; Youn et al., 2016). Besides, cultures might differ in
the way caregivers talk to children (Cristia, Dupoux, Gurven, \&
Stieglitz, 2017; Kuhl et al., 1997), and this difference in the input
could influence the way in which the children's networks grow. Thus,
cross-linguistic comparison is crucial to test what growth mechanism is
cognitively universal and is used by all children, and what mechanism is
specific to some patterns of learning that emerge due to the particulars
of a given language or culture (Bates \& MacWhinney, 1987; Slobin,
2014).

@@

Figures \ref{fig:corrProd} and \ref{fig:corrComp} show how the age of
production and comprehension, respectively, correlates with the degree
(or indegree for the semantic networks). For ease of visual comparison,
the predictor (i.e., the degree) was centered and scaled. The plots
show, overall, a negative correlation between the month of acquisition
and the degree. In production data, the average correlation across
languages was -0.24 (\(SD=\) 0.10) for the semantic networks and -0.30
(\(SD=\) 0.05) for the phonological networks. In comprehension data, the
average correlation was -0.21 (\(SD=\) 0.08) for the semantic networks
and -0.21 (\(SD=\) 0.07) for the phonological networks. These results
indicate that nouns with higher degrees are generally learned earlier,
thus replicating previous findings in English (Hills et al., 2009;
Storkel, 2009) and extending these findings to 10 different languages,
generally, in both production- and comprehension-based vocabularies.

@@

\hypertarget{ref-lupyan2017}{}
Lupyan, G., \& Lewis, M. (2017). From words-as-mappings to
words-as-cues: The role of language in semantic knowledge.
\emph{Language, Cognition and Neuroscience}.

\hypertarget{ref-macwhinney2014}{}
MacWhinney, B. (2014). \emph{The CHILDES project: Tools for analyzing
talk, Volume II}. Psychology Press.
